Tracing the Stellar Halos of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-07-01 draft/paper1_v12.tex
Small edits

    Finally, we emphasize that in this work, we do not attempt to disentangle the 
    galaxy light from any ``intra-cluster'' light component (ICL; e.g. 
    \citealt{Carlberg1997, Lin2004, Gonzalez2005, Mihos2005}). 
    Although the rising stellar velocity dispersion in the outskirt of massive BCG
    hints a kinematically separated ICL component (e.g. 
    \citealt{Dressler1979, Carter1999, Kelson2002, Bender2015, Longobardi2015}),
    it is extremely difficult to reliably isolate them photometrically.
    Moreover, both the stellar halo of main galaxy and the ICL component carry 
    important information regarding the assembly history of central galaxy and its 
    dark matter halo. 
    Therefore, we adopt the view that the light of the main galaxy and the 
    ICL component share a smooth and continuous distribution.

@@

    \citet{Patel2013} extracted a median \mden{} profile for massive ETGs at 
    $0.25 < z < 0.50$ using stacked \textit{HST}/ACS images. 
    These galaxies are selected at a constant cumulative number density and are 
    thought to be the progenitors of $z=0$ massive ETGs (e.g. \citealt{Leja2013}).  
    The median \mstar{} of the \citet{Patel2013} sample is 
    ${\sim} 10^{11.2} M_{\odot}$ which is lower than our lowest mass bin. 
    However, \citet{Patel2013} uses the BC03 stellar population model which leads to 
    \mstar{} that are roughly 0.1 dex lower than our FSPS estimates 
    (see Appendix~\ref{app:sed}). 
    Furthermore, the \citet{Patel2013} images are shallower than ours which means 
    that their \mstar{} could still be underestimated due to missing light in the 
    outskirts. 
    Given these two considerations, it is reasonable to roughly compare the 
    \citet{Patel2013} profile with the one in our lowest \mtot{} bin. 
    The superb resolution of the \textit{HST}/ACS image allows \citet{Patel2013} to 
    accurately measure \mden{} profile down to 1 kpc without worrying the smearing 
    effect of seeing. 
    The good agreement between our profiles and the ones derived from HST imaging 
    demonstrates that our profiles are robust at $r\geq 3$ kpc so that we can 
    accurately measure \minn{}.

@@

        \item The inner component of $z{\sim} 0$ ellipticals from the 2-D 
            decomposition of \citet{Huang2013a}. 
            \citet{Huang2013b} showed that this inner component is structurally 
            similar to the compact ``red nuggets'' at high-$z$.

@@

    In this work, we study how the stellar mass density profiles and other structural
    properties of massive central galaxies depend on their total stellar mass using 
    deep images from the Subaru HSC survey. 
    With the help of this high-quality and wide area data set, we directly map the 
    stellar mass distributions of ${\sim}7000$ massive central galaxies at 
    $0.3 < z < 0.5$ out to $>100$ kpc without resorting to stacking techniques. 
    We group massive central galaxies into two categories based on their host halo 
    mass (\mhalo{}$\simgt 10^{14.0} M_{\odot}$ and \mhalo{}$\simlt 10^{14} M_{\odot}$)
    and three bins of \mtot{}.  
    Our main results are:

>>>>

    Finally, we emphasize that in this work, we do not attempt to disentangle the 
    galaxy light from any ``intra-cluster'' light component (ICL; e.g. 
    \citealt{Carlberg1997, Lin2004, Gonzalez2005, Mihos2005}). 
    Although the rising stellar velocity dispersion in the outskirt of massive 
    brightest cluster galaxy (BCG)
    hints a kinematically separated ICL component (e.g. 
    \citealt{Dressler1979, Carter1999, Kelson2002, Bender2015, Longobardi2015}),
    it is extremely difficult to reliably isolate them photometrically.
    Moreover, both the stellar halo of main galaxy and the ICL component carry 
    important information regarding the assembly history of central galaxy and its 
    dark matter halo. 
    Therefore, we adopt the view that the light of the main galaxy and the 
    ICL component share a smooth and continuous distribution.

@@

    \citet{Patel2013} extracted a median \mden{} profile for massive ETGs at 
    $0.25 < z < 0.50$ using stacked \textit{HST}/ACS images. 
    These galaxies are selected at a constant cumulative number density and are 
    thought to be the progenitors of $z=0$ massive ETGs (e.g. \citealt{Leja2013}).  
    The median \mstar{} of the \citet{Patel2013} sample is 
    ${\sim} 10^{11.2} M_{\odot}$ which is lower than our lowest mass bin. 
    However, \citet{Patel2013} uses the BC03 stellar population model which leads to 
    \mstar{} that are roughly 0.1 dex lower than our FSPS estimates 
    (see Appendix~\ref{app:sed}). 
    Furthermore, the \citet{Patel2013} images are shallower than ours which means 
    that their \mstar{} could still be underestimated due to missing light in the 
    outskirts. 
    Given these two considerations, it is reasonable to roughly compare the 
    \citet{Patel2013} profile with the one in our lowest \mtot{} bin. 
    The superb resolution of the \textit{HST}/ACS images allows \citet{Patel2013} to 
    accurately measure \mden{} profile down to 1 kpc without worrying the smearing 
    effect of seeing. 
    The good agreement between our profiles and the ones derived from HST imaging 
    demonstrates that our profiles are robust at $r\geq 3$ kpc so that we can 
    accurately measure \minn{}.

@@

        \item The inner component of $z{\sim} 0$ ellipticals from the 2-D 
            decomposition of \citet{Huang2013a}. 
            \citet{Huang2013b} show that this inner component is structurally 
            similar to the compact ``red nuggets'' at high-$z$.

@@

    In this work, we study how the projected stellar mass density profiles and other 
    structural properties of massive central galaxies depend on their total stellar 
    mass using deep images from the Subaru HSC survey. 
    With the help of this high-quality and wide area data set, we directly map the 
    stellar mass distributions of ${\sim}7000$ massive central galaxies at 
    $0.3 < z < 0.5$ out to $>100$ kpc without resorting to stacking techniques. 
    We group massive central galaxies into two categories based on their host halo 
    mass (\mhalo{}$\simgt 10^{14.0} M_{\odot}$ and \mhalo{}$\simlt 10^{14} M_{\odot}$)
    and three bins of \mtot{}.  
    Our main results are:
